Residence time, a master variable for a more temporal ecology

### 2015-06-27 paper/Manuscript.Rmd
modified bide and main model code, added new data files, conducted new analyses, and added new .Rmd and .pdfs -KL

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
rads <- list()
rad.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/RADs.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)

rad.list[is.na(rad.list)] <- 0
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
species <- list()
species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/18_June_3/Species.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)

species.list[is.na(species.list)] <- -1
```

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
#install.packages("vegan") 
require("vegan") 
#install.packages("moments")
require("moments")
```

@@

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Loading simulated RADs and species lists

rad.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/RADs.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)
rad.list[is.na(rad.list)] <- 0

species.list <- read.table("~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/Species.csv",
            header = FALSE, sep = ",", col.names = paste0("V", seq_len(1000)),
            as.is = TRUE, skipNul = TRUE, fill = TRUE)
species.list[is.na(species.list)] <- -1
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Loading simulated data csv files

sims <- c()
cts <- c()
tracer.RTDs <- list()
res.RTDs <- list()
ind.RTDs <- list()

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/IndRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  cts <- c(cts, line[1])
  sims <- c(sims, line[2])
  rtd <- line[-1:-2]
  ind.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/TracerRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  tracer.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)

inputFile <- "~/GitHub/hydrobide/results/simulated_data/2015_June/26_June/ResRTD.csv"
con  <- file(inputFile, open = "r")
ct = 1
while (length(myLine <- scan(con, what="numeric", nlines=1, sep=',', skip=0, quiet=TRUE)) > 0 ){
  line <- as.numeric(myLine)
  rtd <- line[-1:-2]
  res.RTDs[[ct]] <- rtd
  ct <- ct + 1
  } 
close(con)
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
par(mfrow=c(2, 2))

t.skews <- c()
i.skews <- c()
r.skews <- c()
t.means <- c()
i.means <- c()
r.means <- c()

colors <- rainbow(length(ind.RTDs))
plot(density(log(tracer.RTDs[[1]])), col = 'white', xlab='Residence Time', ylab='Probability Density', xlim = c(0, 8), ylim = c(0, 2),  main = "Tracer RTD")

ct <- 1
for(rtd in tracer.RTDs){
  if(any(is.na(rtd)) == FALSE){
    lines(density(log(rtd), bw = 0.2), col = colors[ct])
    t.skews <- c(t.skews, skewness(rtd))
    t.means <- c(t.means, mean(rtd))
    }
  ct = ct + 1
}

plot(density(log(ind.RTDs[[1]])), col = 'white', xlab='Residence Time', ylab='Probability Density', xlim = c(0, 8), ylim = c(0, 2), main = "Individual RTD")

ct <- 1
for(rtd in ind.RTDs){
  if(any(is.na(rtd)) == FALSE){
    lines(density(log(rtd), bw = 0.2), col = colors[ct])
    i.skews <- c(i.skews, skewness(rtd))
    i.means <- c(i.means, mean(rtd))
    }
  ct = ct + 1
}

plot(density(log(ind.RTDs[[1]])), col = 'white', xlab='Residence Time', ylab='Probability Density', xlim = c(0, 8), ylim = c(0, 2), main = "Resource RTD")

ct <- 1
for(rtd in res.RTDs){
  if(any(is.na(rtd)) == FALSE){
    lines(density(log(rtd), bw = 0.2), col = colors[ct])
    r.skews <- c(r.skews, skewness(rtd))
    r.means <- c(r.means, mean(rtd))
    }
  ct = ct + 1
}
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
par(mfrow=c(1, 1))

plot(log(t.means), t.skews, col = 'darkmagenta', xlab='mean', ylab='skewness', xlim = c(1, 8), ylim = c(-1.2, 3), lwd=2, 
     main = "Most RTD's are right-skewed,\n(many short-lived, few long-lived)")

points(log(i.means),i.skews, lwd=2, col = 'darkcyan')
points(log(r.means), r.skews, lwd=2, col = 'black')

legend("topright", legend = c("tracers", "individuals", "resources"), pch=20, bty = "o", col = c("darkmagenta", "darkcyan", "black"))
```
